Eurovision **Dance** Contest 2008

### 2021-05-05 inst/eurodance.Rmd
more work

The file `eurodance_2008.txt`, used below, is copied from
"Eurovision Dance Contest 2008," Wikipedia, accessed March 31, 2021.
First we specify the matrix as appearing in the Wikipedia page:

```{r, specifymatrix}
eurodance_table <- as.matrix(read.table("eurovision_dance_2008.txt"))
eurodance_table
o <- eurodance_table # saves typing
```

@@

Note the dominance of Poland.  Now we consider the jury's vote:

>>>>

The file `eurodance2008.txt`, used below, is copied from
"Eurovision Dance Contest 2008", Wikipedia, accessed March 31, 2021.
First we specify the matrix as appearing in the Wikipedia page:

```{r, specifymatrix}
eurodance_table <- as.matrix(read.table("eurodance2008.txt"))
eurodance_table
o <- eurodance_table # saves typing
```

@@

Note the dominance of Poland.  We verify consistency:

```{r,cache=TRUE}
consistency(eurodance)
```

Now we consider the jury's vote:
